### 2018-09-26 FrascatiPlot/Paper/aps/main.tex
Another small review to reduce some text here and there. Also, removed appendices and references to them

%\subsection{Simple coalescence}
In the coalescence picture, nucleons produced in the collision coalesce into nuclei if they are close in space and have similar velocities \cite{Butler:1963,Kapusta:1980}. 
For a nucleus with mass number $A = Z + N$, the coalescence probability is typically quantified in terms of the coalescence parameter $B_{A}$.
%that is defined as 
%\begin{equation}
%E_{A}\frac{\mathrm{d}^{3}N_{A}}{\mathrm{d}p_{A}^{3}}=B_{A}{\left(E_{\mathrm{p}}\frac{\mathrm{d}^{3}N_{\mathrm{p}}}{\mathrm{d}p_{\mathrm{p}}^{3}}\right)^{Z}\left\vert_{\vec{p}_{\mathrm{p}}=\frac{\vec{p}_{A}}{A}} \right.\;
%   \left(E_{\mathrm{n}}\frac{\mathrm{d}^{3}N_{\mathrm{n}}}{\mathrm{d}p_{\mathrm{n}}^{3}}\right)^{N}}\left\vert_{\vec{p}_{\mathrm{n}}=\frac{\vec{p}_{A}}{A}} \right.\;
%,    
%\label{eq:BA}
%\end{equation}
%\noindent where $p_{\mathrm{p,n}}$ are the momenta of the proton and neutron and $E_{p,n}$ their energies.
%Since in the LHC collision energy regime the number of produced protons and neutrons at midrapidity is expected to be equal, the equation simplifies to 
Considering that in the LHC collision energy regime the number of produced protons and neutrons at midrapidity is expected to be equal,  $B_{A}$ is defined as

@@

Moreover, the LHC is particularly suited for the production of anti-nuclei, since the number of baryons and anti-baryons is essentially equal at midrapidity \cite{Abbas:2013rua}. As a consequence, also the anti-particle to particle ratio for the light (hyper-)nuclei considered in this work is measured to be consistent with unity in pp, p--Pb and Pb--Pb collisions \cite{ALICE:nucleipp2017, anielski-HQ14, Acharya:2017dmc, Adam:2015yta}.
In a simple coalescence approach, the coalescence parameter is expected to be independent of \pt~and of the object size with respect to the volume of particle emission (hereafter referred to as ``source volume'' or ``source size'').
In this naive expectation, the number of nuclei produced by coalescence increases with increasing number of nucleons produced in the collision. If the nucleon number increases with the event multiplicity, so does the number of (anti-)nuclei. 
While this picture is found to be approximately valid in pp and \pPb~collisions \cite{ALICE:nucleipp2017, anielski-HQ14}, it breaks down in \PbPb~collisions, that exhibit a strong decrease of $B_{A}$ with centrality \cite{ALICE:deuteronppPbPb2015}. 
In addition, the elliptic flow of deuterons cannot be explained by simple coalescence \cite{Acharya:2017dmc}.

@@

The quantum-mechanical nature of the coalescence products is explicitly accounted for by means of an average quantum-mechanical correction factor, $\langle C_{A} \rangle$. In the case of the deuteron, the quantum-mechanical correction factor $\langle C_{d} \rangle$ has been approximated as

@@

Experimentally, the size of the effective volume can be controlled by selecting different collision geometries, i.e. different centrality classes \cite{Abelev:2013qoq}. In heavy-ion collisions the HBT radii are known to scale with the cubic root of the average charged particle multiplicity density \avdNdeta$^{1/3}$ \cite{Adam:2015vna}, and to depend on the pair average transverse momentum $\langle k_{\mathrm{T}}\rangle$ \cite{Aamodt:2011mr}. We make the simplifying assumption that the scaling with \avdNdeta$^{1/3}$ holds across collision systems, which is approximately fulfilled in data \cite{Adam:2015pya}. In contrast to \cite{Blum:2017qnn}, we therefore do not explicitly use the measured HBT radii in our study, but we derive the radii from the measured \avdNdeta~according to the following relation:

@@

\begin{figure}[htbp]
\begin{center}
\includegraphics[width=1\columnwidth]{../HbtRadiusParam.png}
\caption{Parameterisation of the dependence of the source radius on multiplicity assumed in this paper, compared to HBT data from \cite{Adam:2015vna, Adam:2015pya, Abelev:2012sq}. The radius $R$ and the parameters $a$ and $b$ are in units of fm. Parameterisation A is shown here, see text for details.}
\label{fig:radiiparam}
\end{center}
\end{figure}

@@

In the statistical-thermal approach, the yields (d$N$/d$y$) of light anti- and hyper-nuclei are very sensitive to the chemical freeze-out temperature $T_{chem}$ due to their large mass $m$ and approximately scale as d$N$/d$y \propto \exp(-m/T_{chem})$. 
%As a matter of fact, the chemical freeze-out temperature defines the only scale in this model, since 
At the LHC the chemical potentials which ensure the conservation of baryon number ($\mu_{B}$), strangeness ($\mu_{S}$), and electric charge ($\mu_{Q}$) are negligible.
In contrast to the coalescence approach, the statistical-thermal model \cite{Petran:2013dva,Wheaton:2004qb,Andronic:2005yp} provides only \pt-integrated yields. 
%and not the \pt-differential hadron spectra. 
%In order to fill this gap, and for the purpose of this exercise, 
Therefore, \pt~spectra have been modelled using a blast-wave~\cite{Schnedermann:1993ws} parameterization. When extracting the predicted spectrum for a given particle species (proton, $\Lambda$, deuteron, \hethree), the parameters of the blast-wave (average radial flow velocity $\langle\beta_{T}\rangle$, kinetic freeze-out temperature $T_{kin}$, and velocity profile $n$) are fixed to the values obtained from the simultaneous fit to the pion, kaon and proton spectra measured in Pb--Pb collisions as a function of centrality by ALICE~\cite{Abelev:2013vea}. 
The normalisation is fixed using the \pt-integrated deuteron-to-pion ratio and \hethree-to-pion ratio predicted by the GSI-Heidelberg model with $T_{chem} = 156$ MeV, multiplied by the pion yield measured by ALICE~\cite{Abelev:2013vea}. 
This choice, as opposed to using the ratio to proton, is motivated by the fact that the measured proton yield is seen to be slightly overestimated by the thermal model predictions at the LHC~\cite{Abelev:2012wca}.
In the case of hyper-triton, a slightly different procedure is chosen, namely the normalisation for \hthreelambda~is extracted from the statistical-thermal model prediction of the strangeness population factor $S_{3} = { _{\Lambda}^{3}\mathrm{H} / ^{3}{\mathrm{He}} \over \Lambda/p}$ multiplied by the measured $\Lambda/p$ ratio~\cite{Abelev:2013vea,Abelev:2013xaa} and the measured \hethree~yield~\cite{ALICE:deuteronppPbPb2015}. Based on the spectra obtained in this way, we calculate the corresponding coalescence parameters for a given \pt/$A$ and compare it with coalescence expectations. 
%Because we use experimental data to constrain the blast-wave prediction as well as the normalisation, and because such data are provided for given centrality classes, 
We use the corresponding \avdNdeta~in each class to estimate the system radius based on the parameterisation discussed in Sec.~\ref{SecSourceVolume}. 
%In contrast to 
Whereas the coalescence approach
%, which 
explicitly depends on the size of the produced object with respect to the system size, the object size does not enter in the formulation of the blast-wave model.
%Being a simplified hydrodynamic model, the latter treats the system as a continuum and is not particle based. 
The thermal model on the other hand, implements eigenvolume corrections by fixing the object radius as an external parameter %(0.3 fm in the case of baryons for the GSI-Heidelberg model used here).
(0.3 fm for baryons in the GSI-Heidelberg model \cite{Andronic:2017}).
 We refer to the literature for the extensive discussions on the validity of the eigenvolume correction for light (anti-)(hyper-)nuclei~\cite{Vovchenko:2016mwg} and the relation with the possible production of these objects as compact quark bags~\cite{Andronic:2017}.

@@

Data on anti- and hyper-nuclei production at LHC energies and different collision systems have been released by the ALICE Collaboration in recent years \cite{ALICE:nucleipp2017,ALICE:deuteronppPbPb2015,Acharya:2017dmc, Adam:2015yta}. 
In Fig. \ref{fig:CompareB2B3forDifferentParamWithData} we compare the coalescence parameter for deuteron (\btwo) from the coalescence model (see Eqs.~\ref{eq:B2cd} and \ref{eq:B2approx}, with $r_{d} = 3.2$ fm) to the ALICE data for Pb-Pb collisions at $\sqrt{s_{\mathrm{NN}}} = 2.76$ TeV and pp collisions at $\sqrt{s} = 7$ TeV. For pp collisions, data in  \cite{ALICE:nucleipp2017} are given for inelastic (INEL) collisions. In order to facilitate the comparison with future multiplicity-dependent data given in the INEL$>$0 class, we have rescaled the \btwo~and \bthree~by the ratio of the charged particle multiplicity density in these two event classes \cite{Adam:2015gka}.
First, the parameterisation of the system radius fitted to the HBT data as described in Sec.~\ref{SecSourceVolume} (labeled in the following as ``parameterisation A") is used to map the \avdNdeta~to the source size (top left panel of Fig. \ref{fig:CompareB2B3forDifferentParamWithData}). 
We notice that the coalescence volume from parameterisation A leads to discrepancies with respect to the curve from the coalescence calculation, and in particular, we notice that the model would require a larger radius for a given value of \btwo~for Pb-Pb collisions.

@@

\subsection{Thermal and coalescence model for $\mathbf{A = 2, 3}$ anti- and hyper-nuclei}
In Fig.~\ref{fig:CompareThermalAndCoalescence}, the available data for (anti-)deuterons, \mbox{(anti-)}\hethree\ and (anti-)\hthreelambda~\cite{Adam:2015yta} are compared to coalescence and to the thermal model+blast wave predictions described in Sec.~\ref{sec:thermal}.
%both coalescence and thermal model predictions. 
%For the coalescence predictions, 
For the latter and for data, the radius parameterisation B is used, as discussed in Sec.~\ref{sec:radiiParamet}. 
%The combined thermal model and blast-wave predictions are calculated as described in Sec.~\ref{sec:thermal}. 
%As a first observation, one sees that 
For deuterons, both approaches lead to similar predictions and give a reasonable description of the experimental data for $R \gtrsim 1.6$ fm. 
For \hethree~the two models exhibit a qualitatively similar trend as a function of $R$, but they differ by a factor of about 1.5 to 2. The limited amount of data that is currently available is consistent with both models within 2$\sigma$ to 3$\sigma$, where $\sigma$ is the total uncertainty on the data. 
Both approaches show large differences (a factor 5 to 6 for central Pb--Pb collisions and a factor larger than 50 for small radii, $R < 2$ fm) for the \hthreelambda\ caused by the significantly larger size of \hthreelambda\ with respect to \hethree. 
%As a matter of fact, 
The only data point available so far in Pb--Pb collisions is in agreement with the thermal model but not with coalescence. 
The difference between data and the coalescence model is about 6$\sigma$,
%However, it is to be kept in mind that the considerations expressed here are subject to the validity of our assumptions, \textit{in primis} the usage of a gaussian form for the wave-function.
albeit the validity of our assumptions (\textit{in primis} the usage of a gaussian wave-function).
%
%Some authors argue that the difference of data to the coalescence model might be explained by a later formation through the coalescence of $\Lambda$s and deuterons~\cite{Zhang:2018euf}. 
%In addition, the presence of an excited state with $J=3/2$ of the hyper-triton would significantly enhance the phase space for its production. This is not considered here as there is no evidence for the existence of such an excited state~\cite{Mart:1996ay}. According to our understanding, in both the coalescence and the thermal model calculations the presence of excited states enters via a spin degeneracy factor $(2J_{A}+1)$ and thus the predictions would increase by the same factor.
%
In \cite{Zhang:2018euf} it is argued that the difference between data and the coalescence model might be explained by a later formation through the coalescence of $\Lambda$s and deuterons. 
A possible difference attributable to the presence of excited states with $J=3/2$ of \hthreelambda, which would significantly enhance the phase space for its production, is not considered here as there is no evidence for its existence~\cite{Mart:1996ay}.

Most importantly, Fig.~\ref{fig:CompareThermalAndCoalescence} shows that the difference between the two approaches increases with decreasing source volume, thus underlining the need for additional and more precise data as a function of multiplicity or centrality in order to distinguish between the two production scenarios. 
In the case of \hthreelambda~we have considered also a prediction from coalescence for a wider wave-function (dashed line in bottom right panel of Fig. \ref{fig:CompareThermalAndCoalescence}), which results in even lower production probabilities. This behaviour highlights the unique potential to constrain the wave-function of the particle under study at the moment of its production via precise measurements of the coalescence parameter as a function of the source volume. The curves presented here also explicitly allow for an estimate of the expected hyper-triton production in pp collisions, which is expected to be suppressed by about two orders of magnitude with respect to the production of \hethree, thus making this measurement a prime candidate for future experimental studies.

>>>>

%\subsection{Simple coalescence}
In the coalescence picture, nucleons produced in the collision coalesce into nuclei if they are close in space and have similar velocities \cite{Butler:1963,Kapusta:1980}. 
For a nucleus with mass number $A = Z + N$, the coalescence probability is typically quantified in terms of the coalescence parameter $B_{A}$.
%that is defined as 
%\begin{equation}
%E_{A}\frac{\mathrm{d}^{3}N_{A}}{\mathrm{d}p_{A}^{3}}=B_{A}{\left(E_{\mathrm{p}}\frac{\mathrm{d}^{3}N_{\mathrm{p}}}{\mathrm{d}p_{\mathrm{p}}^{3}}\right)^{Z}\left\vert_{\vec{p}_{\mathrm{p}}=\frac{\vec{p}_{A}}{A}} \right.\;
%   \left(E_{\mathrm{n}}\frac{\mathrm{d}^{3}N_{\mathrm{n}}}{\mathrm{d}p_{\mathrm{n}}^{3}}\right)^{N}}\left\vert_{\vec{p}_{\mathrm{n}}=\frac{\vec{p}_{A}}{A}} \right.\;
%,    
%\label{eq:BA}
%\end{equation}
%\noindent where $p_{\mathrm{p,n}}$ are the momenta of the proton and neutron and $E_{p,n}$ their energies.
%Since in the LHC collision energy regime the number of produced protons and neutrons at midrapidity is expected to be equal, the equation simplifies to 
Considering that at LHC energies the number of produced protons and neutrons at midrapidity is expected to be equal,  $B_{A}$ is defined as

@@

Moreover, the LHC is particularly suited for the production of anti-nuclei, since the number of baryons and anti-baryons is essentially equal at midrapidity \cite{Abbas:2013rua}. As a consequence, the anti-particle to particle ratio for the (hyper-)nuclei considered in this work is measured to be consistent with unity in pp, p--Pb and Pb--Pb collisions \cite{ALICE:nucleipp2017, anielski-HQ14, Acharya:2017dmc, Adam:2015yta}.
In a simple coalescence approach, the coalescence parameter is expected to be independent of \pt~and of the object size with respect to the volume of particle emission (hereafter referred to as ``source volume'' or ``source size'').
In this naive expectation, the number of nuclei produced by coalescence increases with increasing number of nucleons produced in the collision. If the nucleon number increases with the event multiplicity, so does the number of (anti-)nuclei. 
While this picture is found to be approximately valid in pp and \pPb~collisions \cite{ALICE:nucleipp2017, anielski-HQ14}, it breaks down in \PbPb~collisions, which exhibit a strong decrease of $B_{A}$ with centrality \cite{ALICE:deuteronppPbPb2015}. 
In addition, the elliptic flow of deuterons cannot be explained by simple coalescence \cite{Acharya:2017dmc}.

@@

The quantum-mechanical nature of the coalescence products is explicitly accounted for by means of an average correction factor, $\langle C_{A} \rangle$. In the case of the deuteron, the quantum-mechanical correction factor $\langle C_{d} \rangle$ has been approximated as

@@

Experimentally, the size of the effective volume can be controlled by selecting different collision geometries, i.e. different centrality classes \cite{Abelev:2013qoq}. In heavy-ion collisions the HBT radii are known to scale with the cubic root of the average charged particle multiplicity density \avdNdeta$^{1/3}$ \cite{Adam:2015vna}, and to depend on the pair average transverse momentum $\langle k_{\mathrm{T}}\rangle$ \cite{Aamodt:2011mr}. We make the simplifying assumption that the scaling with \avdNdeta$^{1/3}$ holds across collision systems, which is approximately fulfilled in data \cite{Adam:2015pya}. 
In contrast to \cite{Blum:2017qnn}, we do not explicitly use the measured HBT radii in our study, but we derive the radii from the measured \avdNdeta~according to the following relation:

@@

\begin{figure}[htbp]
\begin{center}
\includegraphics[width=1\columnwidth]{../HbtRadiusParam.png}
\caption{Parameterisation A (details in text) of the dependence of the source radius on multiplicity assumed in this paper, compared to HBT data from \cite{Adam:2015vna, Adam:2015pya, Abelev:2012sq}. The radius $R$ and the parameters $a$ and $b$ are in units of fm.}
\label{fig:radiiparam}
\end{center}
\end{figure}

@@

In the statistical-thermal approach, the yields (d$N$/d$y$) of light anti- and hyper-nuclei are very sensitive to the chemical freeze-out temperature $T_{chem}$ due to their large mass $m$ and approximately scale as d$N$/d$y \propto \exp(-m/T_{chem})$. 
%As a matter of fact, the chemical freeze-out temperature defines the only scale in this model, since 
At the LHC the chemical potentials which ensure the conservation of baryon number ($\mu_{B}$), strangeness ($\mu_{S}$), and electric charge ($\mu_{Q}$) are negligible.
In contrast to the coalescence approach, the statistical-thermal model \cite{Petran:2013dva,Wheaton:2004qb,Andronic:2005yp} provides only \pt-integrated yields. 
%and not the \pt-differential hadron spectra. 
%In order to fill this gap, and for the purpose of this exercise, 
Therefore, \pt~spectra have been modelled using a blast-wave~\cite{Schnedermann:1993ws} parameterization. When extracting the predicted spectrum for a given particle species (proton, $\Lambda$, deuteron, \hethree), the parameters of the blast-wave 
%(average radial flow velocity $\langle\beta_{T}\rangle$, kinetic freeze-out temperature $T_{kin}$, and velocity profile $n$)
are fixed to the values obtained from the simultaneous fit to the pion, kaon and proton spectra measured in Pb--Pb collisions as a function of centrality by ALICE~\cite{Abelev:2013vea}. 
The normalisation is fixed using the \pt-integrated deuteron-to-pion ratio and \hethree-to-pion ratio predicted by the GSI-Heidelberg model with $T_{chem} = 156$ MeV, multiplied by the pion yield measured by ALICE~\cite{Abelev:2013vea}. 
This choice, as opposed to using the ratio to proton, is motivated by the fact that the measured proton yield is seen to be slightly overestimated by the thermal model predictions at the LHC~\cite{Abelev:2012wca}.
In the case of hyper-triton, the normalisation is extracted from the statistical-thermal model prediction of the strangeness population factor $S_{3} = { _{\Lambda}^{3}\mathrm{H} / ^{3}{\mathrm{He}} \over \Lambda/p}$ multiplied by the measured $\Lambda/p$ ratio~\cite{Abelev:2013vea,Abelev:2013xaa} and \hethree~yield~\cite{ALICE:deuteronppPbPb2015}. Based on the spectra obtained in this way, we calculate the corresponding coalescence parameters for a given \pt/$A$ and compare it with coalescence expectations. 
%Because we use experimental data to constrain the blast-wave prediction as well as the normalisation, and because such data are provided for given centrality classes, 
We use the corresponding \avdNdeta~in each class to estimate the system radius based on the parameterisation discussed in Sec.~\ref{SecSourceVolume}. 
%In contrast to 
Whereas the coalescence approach
%, which 
explicitly depends on the size of the produced object with respect to the system size, the object size does not enter in the formulation of the blast-wave model.
%Being a simplified hydrodynamic model, the latter treats the system as a continuum and is not particle based. 
The thermal model on the other hand, implements eigenvolume corrections by fixing the object radius as an external parameter %(0.3 fm in the case of baryons for the GSI-Heidelberg model used here).
(0.3 fm for baryons in the GSI-Heidelberg model \cite{Andronic:2017}).
 We refer to the literature for the extensive discussions on the validity of the eigenvolume correction for light (anti-)(hyper-)nuclei~\cite{Vovchenko:2016mwg} and the relation with the possible production of these objects as compact quark bags~\cite{Andronic:2017}.

@@

Data on anti- and hyper-nuclei production at LHC energies and different collision systems have been released by the ALICE Collaboration in recent years \cite{ALICE:nucleipp2017,ALICE:deuteronppPbPb2015,Acharya:2017dmc, Adam:2015yta}. 
In Fig.~\ref{fig:CompareB2B3forDifferentParamWithData} we compare the coalescence parameter for deuteron (\btwo) from the coalescence model (see Eqs.~\ref{eq:B2cd} and \ref{eq:B2approx}, with $r_{d} = 3.2$ fm) to the ALICE data for Pb-Pb collisions at $\sqrt{s_{\mathrm{NN}}} = 2.76$ TeV and pp collisions at $\sqrt{s} = 7$ TeV. For pp collisions, data in  \cite{ALICE:nucleipp2017} are given for inelastic (INEL) collisions. In order to facilitate the comparison with future multiplicity-dependent data given in the INEL$>$0 class, we have rescaled the \btwo~and \bthree~by the ratio of the charged particle multiplicity density in these two event classes \cite{Adam:2015gka}.
First, the parameterisation of the system radius fitted to the HBT data as described in Sec.~\ref{SecSourceVolume} (labeled in the following as ``parameterisation A") is used to map the \avdNdeta~to the source size (top left panel of Fig. \ref{fig:CompareB2B3forDifferentParamWithData}). 
We notice that the coalescence volume from parameterisation A leads to discrepancies with respect to the curve from the coalescence calculation, and in particular, we notice that the model would require a larger radius for a given value of \btwo~for Pb-Pb collisions.

@@

\subsection{Thermal and coalescence model for $\mathbf{A = 2, 3}$ anti- and hyper-nuclei}
In Fig.~\ref{fig:CompareThermalAndCoalescence}, the available data for (anti-)deuterons, \mbox{(anti-)}\hethree\ and (anti-)\hthreelambda~\cite{Adam:2015yta} are compared to coalescence and to the thermal model+blast wave predictions described in Sec.~\ref{sec:thermal}.
%both coalescence and thermal model predictions. 
%For the coalescence predictions, 
For the latter and for data, the radius parameterisation B is used, see Sec.~\ref{sec:radiiParamet}. 
%The combined thermal model and blast-wave predictions are calculated as described in Sec.~\ref{sec:thermal}. 
%As a first observation, one sees that 
For deuterons, both approaches lead to similar predictions and give a reasonable description of the experimental data for $R \gtrsim 1.6$ fm. 
For \hethree~the two models exhibit a qualitatively similar trend as a function of $R$, but they differ by a factor of about 1.5 to 2. The limited amount of data that is currently available is consistent with both models within 2$\sigma$ to 3$\sigma$, where $\sigma$ is the total uncertainty on the data. 
Both approaches show large differences (a factor 5 to 6 for central Pb--Pb collisions and a factor larger than 50 for small radii, $R < 2$ fm) for the \hthreelambda\ caused by the significantly larger size of \hthreelambda\ with respect to \hethree. 
%As a matter of fact, 
The only data point available so far in Pb--Pb collisions is in agreement with the thermal model but not with coalescence. 
The difference between data and the coalescence model is about 6$\sigma$,
%However, it is to be kept in mind that the considerations expressed here are subject to the validity of our assumptions, \textit{in primis} the usage of a gaussian form for the wave-function.
albeit the validity of our assumptions (\textit{in primis} the usage of a gaussian wave-function).
%
%Some authors argue that the difference of data to the coalescence model might be explained by a later formation through the coalescence of $\Lambda$s and deuterons~\cite{Zhang:2018euf}. 
%In addition, the presence of an excited state with $J=3/2$ of the hyper-triton would significantly enhance the phase space for its production. This is not considered here as there is no evidence for the existence of such an excited state~\cite{Mart:1996ay}. According to our understanding, in both the coalescence and the thermal model calculations the presence of excited states enters via a spin degeneracy factor $(2J_{A}+1)$ and thus the predictions would increase by the same factor.
%
In \cite{Zhang:2018euf} it is argued that the difference between data and the coalescence model might be explained by a later formation through the coalescence of $\Lambda$s and deuterons. 
A possible difference attributable to the presence of excited states with $J=3/2$ of \hthreelambda, which would significantly enhance the phase space for its production, is not considered here as there is no evidence for its existence~\cite{Mart:1996ay}.

Most importantly, Fig.~\ref{fig:CompareThermalAndCoalescence} shows that the difference between the two approaches increases with decreasing source volume, thus underlining the need for additional and more precise data as a function of multiplicity in order to distinguish between the two production scenarios. 
In the case of \hthreelambda~we have considered also a prediction from coalescence for a wider wave-function (dashed line in bottom right panel of Fig. \ref{fig:CompareThermalAndCoalescence}), which results in even lower production probabilities. This behaviour highlights the unique potential to constrain the wave-function of the particle under study at the moment of its production via precise measurements of the coalescence parameter as a function of the source volume. The curves presented here also explicitly allow for an estimate of the expected hyper-triton production in pp collisions, which is expected to be suppressed by about two orders of magnitude with respect to the production of \hethree, thus making this measurement a prime candidate for future experimental studies.

### 2018-09-26 FrascatiPlot/Paper/aps/table1.tex
Another small review to reduce some text here and there. Also, removed appendices and references to them

\begin{ruledtabular}
\begin{tabular}{cccccccc}\\[-2ex]
Mass number & Nucleus &  Composition  & $B_{E}$ (MeV)   &  $J_{A}$ & \rmsradius$^{meas}$~(fm) &  $r_{A}$ (fm) & Refs. 
\\[0.5ex] \hline \\[-2ex]
      A = 2                     & d                                    & pn                                  &   2.224575 (9)     &     1   & 2.1413 $\pm$ 0.0025      &  3.2    &   \cite{VanDerLeun:1982bhg,Mohr:2015ccw}     \\[0.5ex]  \hline \\[-2ex]
      A = 3  & \tritium 	                  & pnn                               &    8.4817986 (20) & 1/2   &  1.755  $\pm$ 0.086        &  2.15   &   \cite{Purcell:2015gtm}           \\
                                   & \hethree                         & ppn                                &   7.7180428  (23) & 1/2  & 1.959 $\pm$  0.030         &   2.48  &   \cite{Purcell:2015gtm} \\
                                   & \hthreelambda               & p$\Lambda$n                &    0.13 $\pm$ 0.05 & 1/2  &  4.9 --  10.0                    &  6.8 -- 14.1 & \cite{Davis:2005mb,Nemura:1999qp} \\[0.5ex]  \hline \\[-2ex]
                                   A = 4  & \hefour                          & ppnn                              &    28.29566   (20)  &      0  &  1.6755 $\pm$ 0.0028  &  1.9  & \cite{1674-1137-41-3-030003,Angeli:2013epw} \\
                                   & \hfourlambda                & p$\Lambda$nn              &  2.04 $\pm$0.04   &   0   &    2.0 -- 3.8             & 2.4 -- 4.9  & \cite{Davis:2005mb,Nemura:1999qp} \\
                                   & \hfourtwolambda          &  p$\Lambda\Lambda$n &   0.39 -- 0.51         &    1     &    4.2 -- 7.1          & 5.5 -- 9.4  &   \cite{Nemura:1999qp} \\
                                   & \hefourlambda              & pp$\Lambda$n              &  2.39 $\pm$ 0.03  &    0   &    2.0 -- 3.8            & 2.4 -- 4.9  & \cite{Davis:2005mb,Nemura:1999qp}\\[0.5ex]

@@

\caption{Properties of nuclei and hyper-nuclei with mass number $A \leq 4$. $B_{E}$ is the binding energy in MeV, $J_{A}$ is the spin. The size of the nucleus is given in terms of the (charge) rms radius of the wave-function, \rmsradius. The size parameter of the wave-function of the harmonic oscillator potential,  $r_{A}$, is chosen such that the measured/expected rms,  \rmsradius$^{meas}$~(fm), is approximately reproduced. Details are given in Appendix \ref{appendix:Sato}. Please note that the proton rms charge radius $\lambda_{p} = 0.879(8)$ fm \cite{bernauer10} is subtracted quadratically from the measured rms charge radius $\rmsradius^{meas}$ of the nucleus $\rmsradius = \sqrt{(\rmsradius^{meas})^2 - {\lambda_{p}^2}}$ to account for the finite extension of the constituents. Implicitly we assume here that $\lambda_{\Lambda}\approx \lambda_{n}\approx \lambda_{p}$.
 References are given in the last column. The spin of \hfourtwolambda\ is discussed in the text of~\cite{Nemura:1999qp}.}
\label{tab:nucleusradii}
\end{table*}

>>>>

\begin{ruledtabular}
\begin{tabular}{cccccccc}\\[-2ex]
Mass number & Nucleus &  Composition  & $B_{E}$ (MeV)   &  $J_{A}$ & \rmsradius$^{meas}$~(fm) &  $r_{A}$ (fm) & Refs. 
\\[0.5ex] \hline \\[-2ex]
      A = 2                     & d                                    & pn                                  &   2.224575 (9)     &     1   & 2.1413 $\pm$ 0.0025      &  3.2    &   \cite{VanDerLeun:1982bhg,Mohr:2015ccw}     \\[0.5ex]  \hline \\[-2ex]
      A = 3  & \tritium 	                  & pnn                               &    8.4817986 (20) & 1/2   &  1.755  $\pm$ 0.086        &  2.15   &   \cite{Purcell:2015gtm}           \\
                                   & \hethree                         & ppn                                &   7.7180428  (23) & 1/2  & 1.959 $\pm$  0.030         &   2.48  &   \cite{Purcell:2015gtm} \\
                                   & \hthreelambda               & p$\Lambda$n                &    0.13 $\pm$ 0.05 & 1/2  &  4.9 --  10.0                    &  6.8 -- 14.1 & \cite{Davis:2005mb,Nemura:1999qp} \\[0.5ex]  \hline \\[-2ex]
                                   A = 4  & \hefour                          & ppnn                              &    28.29566   (20)  &      0  &  1.6755 $\pm$ 0.0028  &  1.9  & \cite{1674-1137-41-3-030003,Angeli:2013epw} \\
                                   & \hfourlambda                & p$\Lambda$nn              &  2.04 $\pm$0.04   &   0   &    2.0 -- 3.8             & 2.4 -- 4.9  & \cite{Davis:2005mb,Nemura:1999qp} \\
                                   & \hfourtwolambda          &  p$\Lambda\Lambda$n &   0.39 -- 0.51         &    1 \cite{Nemura:1999qp}    &    4.2 -- 7.1          & 5.5 -- 9.4  &   \cite{Nemura:1999qp} \\
                                   & \hefourlambda              & pp$\Lambda$n              &  2.39 $\pm$ 0.03  &    0   &    2.0 -- 3.8            & 2.4 -- 4.9  & \cite{Davis:2005mb,Nemura:1999qp}\\[0.5ex]

@@

\caption{Properties of nuclei and hyper-nuclei with mass number $A \leq 4$. $B_{E}$ is the binding energy in MeV, $J_{A}$ is the spin. The size of the nucleus is given in terms of the (charge) rms radius of the wave-function, \rmsradius. The size parameter of the wave-function of the harmonic oscillator potential,  $r_{A}$, is chosen such that the measured/expected rms,  \rmsradius$^{meas}$~(fm), is approximately reproduced. Please note that the proton rms charge radius $\lambda_{p} = 0.879(8)$ fm \cite{bernauer10} is subtracted quadratically from $\rmsradius^{meas}$ of the nucleus $\rmsradius = \sqrt{(\rmsradius^{meas})^2 - {\lambda_{p}^2}}$ to account for the finite extension of the constituents. Implicitly we assume here that $\lambda_{\Lambda}\approx \lambda_{n}\approx \lambda_{p}$.}
 %References are given in the last column.}
%. The spin of \hfourtwolambda\ is discussed in the text of~\cite{Nemura:1999qp}.
\label{tab:nucleusradii}
\end{table*}
